%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Short Sectioned Assignment
% LaTeX Template
% Version 1.0 (5/5/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Frits Wenneker (http://www.howtotex.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[paper=a4, fontsize=11pt]{scrartcl} % A4 paper and 11pt font size

\usepackage[T1]{fontenc} % Use 8-bit encoding that has 256 glyphs
\usepackage{fourier} % Use the Adobe Utopia font for the document - comment this line to return to the LaTeX default
\usepackage[english]{babel} % English language/hyphenation
\usepackage{amsmath,amsfonts,amsthm} % Math packages
\usepackage{graphicx} % figures
\usepackage{listings} % Required for insertion of code

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage{sectsty} % Allows customizing section commands
\allsectionsfont{\centering \normalfont\scshape} % Make all sections centered, the default font and small caps

\usepackage{fancyhdr} % Custom headers and footers
\pagestyle{fancyplain} % Makes all pages in the document conform to the custom headers and footers
\fancyhead{} % No page header - if you want one, create it in the same way as the footers below
\fancyfoot[L]{} % Empty left footer
\fancyfoot[C]{} % Empty center footer
\fancyfoot[R]{\thepage} % Page numbering for right footer
\renewcommand{\headrulewidth}{0pt} % Remove header underlines
\renewcommand{\footrulewidth}{0pt} % Remove footer underlines
\setlength{\headheight}{13.6pt} % Customize the height of the header

\numberwithin{equation}{section} % Number equations within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{figure}{section} % Number figures within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)
\numberwithin{table}{section} % Number tables within sections (i.e. 1.1, 1.2, 2.1, 2.2 instead of 1, 2, 3, 4)

\setlength\parindent{0pt} % Removes all indentation from paragraphs - comment this line for an assignment with lots of text

\lstset{
   extendedchars=true,
   basicstyle=\footnotesize\ttfamily,
   showstringspaces=false,
   showspaces=false,
   numbers=left,
   numberstyle=\footnotesize,
   numbersep=10pt,
   tabsize=4,
   breaklines=true,
   showtabs=false,
   captionpos=b
}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\newcommand{\horrule}[1]{\rule{\linewidth}{#1}} % Create horizontal rule command with 1 argument of height

\title{	
\normalfont \normalsize 
\textsc{Udacity Data Analyst Nanodegree} \\ [25pt] % Your university, school and/or department name(s) % OVERRIDE
\horrule{0.5pt} \\[0.4cm] % Thin top horizontal rule
\LARGE{Project 1} \\ % The assignment title % SIZE OVERRIDE
\horrule{0.5pt} \\[0.5cm] % Thick bottom horizontal rule
}

\author{Ming Wen} % Your name % OVERRIDE

\date{\normalsize\today} % Today's date or a custom date

\begin{document}

\maketitle % Print the title

%----------------------------------------------------------------------------------------
%	PROBLEM 1
%----------------------------------------------------------------------------------------

\section{Test a Perceptual Phenomenon}

\subsection{Idenfity variables in the experiment}
\medskip
\noindent\fbox{
	\parbox{\textwidth}{
        What is our independent variable?
        What is our dependent variable?
	}
}
\medskip

In this experiment, the independent variable is congruence or
incongruence of words and colors. The dependent variable is
the time of response under each condition.

\subsection{Establish a hypothesis and statistical test}
\medskip
\noindent\fbox{
	\parbox{\textwidth}{
        What is an appropriate set of hypotheses for this task?
        What kind of statistical test do you expect to perform?
        Justify your choices.
	}
}
\medskip

The null hypothesis $H_0$: the time of response under congruent
condition is greater than or equal to the time of response under
incongruent condition.

The alternative hypothesis $H_A$: the time of response under congruent
condition is less than the time of response under incongruent condition.

Since we don't have information about the mean of population, the t-test
should be used. From common sense we believe that time under
incongruent condition should be greater than time under
congruent condition, so a one-tail test is setup.

\subsection{Report descriptive statistics}
\medskip
\noindent\fbox{
	\parbox{\textwidth}{
        Report some descriptive statistics regarding this dataset.
        Include at least one measure of central tendency and
        at least one measure of variability.
	}
}
\medskip

Here we define some notations of statistics.

\begin{itemize}
    \item $\bar{t_c}$: the mean time under congruent condition
    \item $\bar{t_i}$: the mean time under incongruent condition
    \item $s_c$: the sample standard deviation of time under
        congruent condition
    \item $s_i$: the sample standard deviation of time under
        congruent condition
    \item $n$: the sample size (of either condition)
\end{itemize}

The sample size of each group is 24.

The mean time under congruent condition $\bar{t_c} = 14.05$.
Its sample standard deviation is $s_c = 3.56$.

The mean time under incongruent condition $\bar{t_i} = 22.02$.
Its sample standard deviation is $s_i = 4.80$.

\subsection{Plot the data}
\medskip
\noindent\fbox{
	\parbox{\textwidth}{
        Provide one or two visualizations that show the distribution
        of the sample data. Write one or two sentences noting what you
        observe about the plot or plots.
	}
}
\medskip



\end{document}

